Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-27 edubots_surveys.Rnw
Add acknowledgements

%%% Begin ...
\begin{document}
\SweaveOpts{concordance=TRUE}

@@

All the authors have contributed to the study presented in this manuscript. 
JJM has been the leader...
PAC has...
AMM has ...
FB has...
NA has...
OT has...
AG has...
All authors read and approved the final manuscript.

@@

The authors want to thank to the educators who participated in the survey.
% Antonio - Add other acknowledgements

>>>>

%%% Begin ...
\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

All the authors have contributed to the study presented in this manuscript. 
JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
PAC has...
AMM has ...
FB has...
NA has...
OT has...
AG has...
All authors read and approved the final manuscript.

@@

The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and José Raúl Canay.
% Antonio - Add other acknowledgements
